### 2017-12-24 article.tex
revising section 6

\subsection{Dividend Policy Performed by JD.com}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far JD.com have not declared or paid any dividends on ordinary shares, nor do JD.com have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{See JD.com, Inc. annual report 2016, Page 131}.

>>>>

\subsection{Dividend Policy Performed by JD.com}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far the Group have not declared or paid any dividends on ordinary shares, nor it have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{See JD.com, Inc. annual report 2016, Page 131}. In the light of its heavy financial losses, it is not surprising that the Group Chose not to grant any dividends. The reason why stockholders are willing to purchase and hold the Group's stocks is unlikely for possible dividends. Instead, they may value its dominant position in electronic commerce and look ahead its future development with an optimistic expectation.
